Prefetching SPARQL query cacher

### 2016-05-26 dissertation/cache-proxy.tex
grammar
note problem of SPARQL LDF link

Another persistent script is subscribed to this latter channel. If the
Model supports Linked Data Fragments, a retriever will then download
the results of the triple pattern and enter it into the cache, or use
a single triple pattern SPARQL query if not.

@@

To remedy this problem, we considered creating a custom query planner
for Basic Graph Patterns, but I did not implement it. The outline
would be as follows:
\begin{enumerate}
\item Find triple patterns that are connected with a common variable,
  and group them to ``components''.
\item If a triple pattern have a cached result, create a plan that
  accesses the cache. 
\item If the triple pattern in the previous step caused a Cartesian
  join to be created within a component, create an equivalent
  additional plan for a SPARQL remote evaluation that does not access
  the local cache.
\item Any remaining components consisting of a single triple pattern
  results in a LDF plans.
\item Any remaining components are turned into SPARQL remote BGP
  plans.
\end{enumerate}

>>>>

Another persistent script is subscribed to this latter channel. If the
Model supports Linked Data Fragments, a retriever will then download
the results of the triple pattern and enter it into the cache, or use
a single triple pattern SPARQL query if not. The current
implementation assumes that both and LDF server and a SPARQL endpoint
can be used to answer any triple pattern. Relaxing this assumption
depends on that the LDF specifications gain stronger semantics to link
SPARQL endpoints and LDF servers together. With that, the assumption
could be abandoned trivially.

@@

To remedy this problem, we considered creating a custom query planner
for Basic Graph Patterns, but I did not implement it. The outline
would be as follows:
\begin{enumerate}
\item Find triple patterns that are connected with a common variable,
  and group them to ``components''.
\item If a triple pattern have a cached result, create a plan that
  accesses the cache. 
\item If the triple pattern in the previous step caused a Cartesian
  join to be created within a component, create an equivalent
  additional plan for a SPARQL remote evaluation that does not access
  the local cache.
\item Any remaining components consisting of a single triple pattern
  result in LDF plans.
\item Any remaining components are turned into SPARQL remote BGP
  plans.
\end{enumerate}
